A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-25 elsfrontmatter.tex
more edits

\begin{abstract}
Emission harmonization refers to the process used to match results from
Integrated Assessment Model (IAM) GHG and air pollutants against a common source
of historical emissions trajectories. To date, harmonization has been performed
separately by individual modeling teams. For the hand-over of emission data for
the Shared Socio-economic Pathways (SSPs) to climate model groups, a new
automated automatized approach was developed and used based upon commonly agreed
upon algorithms. This work describes a novel methodology for determining such
harmonization methods and an open-source Python software library implementing
the methodology. Results are shown for two example scenarios (with and without
climate policy cases) using the MESSAGE-GLOBIOM IAM that satisfactorily
harmonize over 96\% of the total emissions trajectories while having a
negligible effect on key long-term climate indicators. This new capability
enhances the comparability across different models, increases transparency and
robustness of results, and allows other teams to easily participate in
intercomparison exercises by using the same harmonization mechansim.
\end{abstract}

>>>>

\begin{abstract}
Emission harmonization refers to the process used to match greenhouse gas (GHG)
and air pollutant results from Integrated Assessment Models (IAMs) against a
common source of historical emissions. To date, harmonization has been performed
separately by individual modeling teams. For the hand-over of emission data for
the Shared Socio-economic Pathways (SSPs) to climate model groups, a new
automated approach based on commonly agreed upon algorithms was developed. This
work describes the novel methodology for determining such harmonization methods
and an open-source Python software library implementing the methodology. Results
are shown for two example scenarios (with and without climate policy cases)
using the MESSAGE-GLOBIOM IAM that satisfactorily harmonize over 96\% of the
total emissions trajectories while having a negligible effect on key long-term
climate indicators. This new capability enhances the comparability across
different models, increases transparency and robustness of results, and allows
other teams to easily participate in intercomparison exercises by using the same
harmonization mechansim.
\end{abstract}
